Framing Effects in the Wild: How the News Media Shapes Public Opinion by Defining Political Issues

### 2022-07-12 paper/Manuscript_Framing.Rmd
Add most crime mig coverage in bild
Revert "get rid of crime model"
This reverts commit fe0ba7197bf2dc195c9ce649ad512a5eb84653b9.
Revert "Revert "get rid of crime model""
This reverts commit 4505cbdc2c051ab3d0103f544f5c23341090ca28.

\center{WORD COUNT: 6,596}

@@

While these findings enable a better understanding about individuals’ susceptibility to framing effects in real-world environments, the literature almost exclusively provides us with experimental evidence. Experiments can only incorporate few characteristics at a time and are limited to emulate a realistic environment for the study of news framing. As Donald Kinder puts it: "[E]xperimental results can always be questioned on their generalizability, and framing effects are no exception. [...] A more balanced reading of frame effects requires methodological diversification, experiments and studies oriented to the world outside" [-@Kinder2007, 157]. In order to test the external validity of framing effect studies, it is necessary to study observational data.

@@

”Framing is the process by which a communication source, such as a news organisation, defines and constructs a political issue or public controversy” [@Nelson1997Rally]. A ”frame” is then the operating unit of this process, defining the issue at hand in a specific way. Different forms of frames have been conceptualised. When I talk about ’frames’ here, I refer to *emphasis frames*. These frames emphasise certain topics in relation to an issue, guiding the recipient to think about the issue with those considerations in mind that are promoted by the frame [@Leeper2020, 152]. For example, issues of increasing welfare contributions might be discussed with reference to inequality and providing chances to the poor, or by mentioning that higher welfare benefits might result in higher taxes. Individuals’ support of a statement will differ dependent on the frame presented [@sniderman2004structure].

@@

```{=tex}
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{vis/CognitiveStorage.png}
    \caption{The cognitive evaluation of an issue $y$ is determined by the strength of association $w_i$ with other concepts with existing evaluations $x_i$.}
    \label{fig:cogStor}
\end{figure}
```

According to this model, framing changes opinions by changing the association of a single consideration with the issue at hand. As a result, a specific consideration factors more prominently in an individuals' attitude formation process: "media frames influence opinions by stressing specific values, facts, or other considerations, endowing them with greater apparent relevance to the issue than they might appear to have under an alternative frame" [@Nelson1997Rally, 569].

@@

@@

@@

EffectPlot(multi = T, scaled = T, boundary_share = 0.2) # 0.2 SD suggested by Peyton 2020, 599

@@

>>>>

WORD COUNT: 6,596

@@

While these findings enable a better understanding about individuals' susceptibility to framing effects in real-world environments, the literature almost exclusively provides us with experimental evidence. Experiments can only incorporate few characteristics at a time and are limited to emulate a realistic environment for the study of news framing. As Donald Kinder puts it: "[E]xperimental results can always be questioned on their generalizability, and framing effects are no exception. [...] A more balanced reading of frame effects requires methodological diversification, experiments and studies oriented to the world outside" [-@Kinder2007, 157]. In order to test the external validity of framing effect studies, it is necessary to study observational data.

@@

"Framing is the process by which a communication source, such as a news organisation, defines and constructs a political issue or public controversy" [@Nelson1997Rally]. A "frame" is then the operating unit of this process, defining the issue at hand in a specific way. Different forms of frames have been conceptualised. When I talk about 'frames' here, I refer to *emphasis frames*. These frames emphasise certain topics in relation to an issue, guiding the recipient to think about the issue with those considerations in mind that are promoted by the frame [@Leeper2020, 152]. For example, issues of increasing welfare contributions might be discussed with reference to inequality and providing chances to the poor, or by mentioning that higher welfare benefits might result in higher taxes. Individuals' support of a statement will differ dependent on the frame presented [@sniderman2004structure].

@@

```{=tex}
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{vis/CognitiveStorage.png}
    \caption{The cognitive evaluation of an issue $y$ is determined by the strength of association $w_i$ with other concepts with existing evaluations $x_i$.}
    \label{fig:cogStor}
\end{figure}
```
According to this model, framing changes opinions by changing the association of a single consideration with the issue at hand. As a result, a specific consideration factors more prominently in an individuals' attitude formation process: "media frames influence opinions by stressing specific values, facts, or other considerations, endowing them with greater apparent relevance to the issue than they might appear to have under an alternative frame" [@Nelson1997Rally, 569].

@@

```{r exampleArticles, results='markup'}

TenMostCrime()

@@

Figure \@ref(fig:multidv) visualizes the standardized effect of the change in framing on relevant dependent variables. As suggested by @Laken2017 [see also @Peyton2020], I added equivalence bounds of 0.2 standard deviations, representing a minimal effect size

@@

EffectPlot(multi = T, scaled = "raw", boundary_share = 0.2) # 0.2 SD suggested by Peyton 2020, 599

@@

## Alternative Dependent Variables

EffectPlot(multi = T, scaled = "raw", boundary_share = 0.2) # 0.2 SD suggested by Peyton 2020, 599

## Stability of Estimates
